A boundary-integral framework to simulate \\ the viscous erosion of a porous medium

### 2018-04-05 docs/methods/erosion_methods.tex
NM

Flow-induced erosion reshapes solid material over a range of scales found in nature, from large-scale land formations \cite{han1969, Rothman2012, coh-dev-sey-yi-szy-rot2015} down to human-scale structures and patterns \cite{daerr2003erosion}. Though less visible, these same forces are at work at the very smallest of scales, slowly deteriorating the individual constituents of porous media (e.g.~solid, sand, or clay) or biological structures like plaque and biofilms \cite{pic-van-hei2000, sha2002, gro-gij-van-fer-hat-van-yua-wen2007}. Motivated by these small-scale applications, we develop here numerical methods to simulate fluid-mechanical erosion of multiple solid bodies in Stokes flow --- the most relevant regime for groundwater flow and the aforementioned biological examples.

@@

The example of an eroding porous medium presents new and interesting opportunities in a few ways. First of all, the medium is composed of many bodies and so multiply-connected domains most be considered. These bodies can interact via the surrounding flow. In particular, Stokes flow enables long-range interactions, which strongly couples the shape evolution of difference bodies.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Related work} The effect of erosion on a geometry is quite
rich.  For instance, it has been hypothesized and numerically observed
that the erosion leads to a shear stress that is uniform on the body
which results in a uniform erosion rate.  The shape that has a uniform
shear stress is analyzed in three dimensions by Montenegro-Johnson and
Lauga~\cite{mon-lau2015} which is an extension of the analysis done by
Pironneau~\cite{pir1973} to find a Stokesian drag minimizing shape.  In
this idealized case, analytical axisymmetric shapes that minimize the
drag can be found.  However, the effect of erosion on a porous media is
less understood.

>>>>

Flow-induced erosion reshapes solid material over a range of scales found in nature, from large-scale land formations \cite{han1969, Rothman2012, coh-dev-sey-yi-szy-rot2015} down to human-scale structures and patterns \cite{daerr2003erosion}. Though less visible, these same forces are at work at the very smallest scales, slowly deteriorating the individual constituents of porous media (e.g.~solid, sand, or clay) or biological structures like plaque and biofilms \cite{pic-van-hei2000, sha2002, gro-gij-van-fer-hat-van-yua-wen2007}. Motivated by these small-scale applications, we develop here numerical methods to simulate fluid-mechanical erosion of multiple solid bodies in Stokes flow --- the most relevant regime for groundwater and bio-fluid applications.

@@

\vsp{2}
The example of an eroding porous medium presents new and interesting opportunities in a few ways. First of all, the medium is composed of many bodies and so multiply-connected domains most be considered. These bodies can interact via the surrounding flow. In particular, Stokes flow enables long-range interactions, which strongly couples the shape evolution of difference bodies.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Related work} The effect of erosion on a geometry is quite
rich.  For instance, it has been hypothesized and numerically observed
that the erosion leads to a shear stress that is uniform on the body
which results in a uniform erosion rate.  The shape that has a uniform
shear stress is analyzed in three dimensions by Montenegro-Johnson and
Lauga~\cite{mon-lau2015} which is an extension of the analysis done by
Pironneau~\cite{pir1973} to find a Stokesian drag minimizing shape. 
\todo[inline]{Double check this statement. I am not sure that the shape found by Lauga has uniform shear stress. The shape found by Pironneau does.}
In this idealized case, analytical axisymmetric shapes that minimize the
drag can be found.  However, the effect of erosion on a porous media is
less understood.
